\begin{thebibliography}{9}

    \bibitem{bell07}
        Bell, Genevieve, and Paul Dourish,
        ``Yesterday's tomorrows: notes on ubiquitous computing's dominant vision'',
        \emph{Personal and Ubiquitous Computing} 11: pp. 133-143,
        2007.
        
    \bibitem{weiser91}
        Weiser, Mark,
        ``The Computer for the 21st Century'',
        \emph{Mobile Computing and Communications Review} 3(3): pp. 3-14,
        1991.
		
	\bibitem{weiser93}
		Weiser, Mark,
		\emph{Some Computer Science Issues in Ubiquitous Computing},
		1993.
		\verb+http://www.ubiq.com/hypertext/weiser/UbiCACM.html+, accessed 07-05-2014.
        
    \bibitem{weiseronline}
        Weiser, Mark,
        \emph{Ubiquitous Computing}.
        \verb+http://www.ubiq.com/hypertext/weiser/UbiHome.html+, accessed 06-05-2014.
        
	\bibitem{weisernomadic}
		Weiser, Mark,
		\emph{Nomadic Issues in Ubiquitous Computing},
		\verb+http://www.ubiq.com/hypertext/weiser/NomadicInteractive/+, accessed 07-05-2014.
		
    \bibitem{cisco}
        Cisco prediction
        \verb+http://www.cisco.com/c/en/us/solutions/collateral/service-provider/visual-networking-index-vni/VNI_Hyperconnectivity_WP.html+, accessed 06-05-2014
        
    \bibitem{wikipedia-mobiles}
    \verb+http://en.wikipedia.org/wiki/Market_share_of_personal_computer_vendors#Unit_sales+ <-- computer sales ! 

    \bibitem{wikipedia-pcs}
    \verb+http://en.wikipedia.org/wiki/List_of_best-selling_mobile_phones#Annual_sales_by_manufacturer+ <-- mobile phone sales
 
\end{thebibliography}